\problemname{Thirsty Cows}

The water level has been changing a lot lately, and there is a thirsty cow by the water that could change that!

You have gotten the information regarding what the water level will be the coming $N$ days. 
On any given day $i$, the water level will be $a_i$. 
If you let the thirsty cow drink water that day, the cow will be able to greedily drink $a_i$ water units. 
By letting the thirsty cow drink, it will also decrease the water level of all days after that by $a_i$ units. 
Note that the cow can only drink when there is a positive amount of water units that day.

Since the thirsty cow is extremly thirsty, the cow wants to drink as much water as possble in total over all $N$ days. 
Could you help the thirsy cow figure out how much it could drink?

\section*{Input}
The first line contains an integer $N$ ($1 \leq N \leq 3 \cdot 10^5$), the number of days as described above.

The second line contains $N$ integers, $a_1, a_2, \dots, a_N$ $(1 \leq a_i \leq 10^9)$, where $a_i$ denotes the water level on the $i$-th day.

\section*{Output}
Print a single integer: the maximum amount of water units the thirsy cow can drink across all $N$ days. 

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. Each test group contains
a set of test cases. To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $19$       & $N \leq 200$ \\ \hline
  $2$    & $29$       & $N \leq 3000$ \\ \hline
  $3$    & $52$       & No additional constraints. \\ \hline
\end{tabular}
