\problemname{Infinity alarm}

It is the last evening of your trip abroad, and you need to get up early tomorrow
to catch your flight. But then you find that your phone is broken and there is no 
other alarm clock in the room. The only possible way to wake yourself up is to make 
your computer overheat at the right moment, which would create a loud noise. You decide 
to do this by coding up a complicated algorithm that after a number of steps creates an 
infinitely large set of numbers.


You are given a set of $N$ positive integers $S$. Let $f(S)$ be the set of positive integers $x$ such 
that there is an odd number of elements in $S$ that are strictly smaller than $x$.

Every second, the set $S$ gets replaced by $f(S)$. Your task is to calculate after
how many seconds the set $S$ is infinitely big.

\section*{Input}
The first line contains one integer $N$ ($1 \leq N \leq 5 \cdot 10^5$).

The second line contains $N$ integers $s_1, s_2, \dots, s_N$ ($1 \leq s_i \leq 10^9$), 
the integers in $S$. These numbers will all be different.

\section*{Output}
Print one integer, the number of seconds until the set $S$ has infinitely many elements.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. Each test group contains
a set of test cases. To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $15$       & $N \leq 2$ \\ \hline
  $2$    & $30$       & $N \leq 100$, $s_i \leq 3 \cdot 10^5$ \\ \hline
  $3$    & $55$       & No additional constraints. \\ \hline
\end{tabular}